---
title       : Comparing Models for Mid-Atlantic Wage Data
subtitle    : Developing Data Products PeerAssessments
author      : yYamamotojp
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Mid-Atlantic Wage Data

Wage Data Variables:

```{r, echo=FALSE}
library(ISLR)
library(ggplot2)
names(Wage)
```

Wage Data Record Example:

```{r, echo=FALSE}
head(Wage, 2)
```

--- .class #id 

## Target and Variable

Relationship Between age and wage

```{r, echo=FALSE}
qplot(age, wage, data=Wage, geom=c("point", "smooth"), method="lm")
```

--- .class #id 

## Models

Trying to compare modles as follow

* Linear Regression: 

* SVM Linear Regression:

* Regression Tree:

--- .class #id 

## Experiment Plan

### Error Metric

* Root Mean Square Error: sqrt(mean((test$y - pred$y)^2))

### Cross Validation 

Train and Test set split size: 6:4

```{r, cache=TRUE}
set.seed(12345)
in.train <- createDataPartition(y=Wage$wage, p=0.6, list=FALSE)
tr.set <- Wage[in.train,]; te.set <- Wage[-in.train,]
c(dim(tr.set), ",", dim(te.set))
```

